Workflow of Inverse Model for Rooting Profiles

### 2020-03-20 Workflow.Rmd
-mortality rates now in % per year -includes Panama traits

```{r Chunk 2.2.0, eval = FALSE}
source("R/4.1.GLUEsetup_part2_BCI.R")
GLUEsetup_part2(growth.type = "med", dbh.residuals = "on", solar.residuals = "off", 
                growth.selection = "size_class_predefined_cc_scaled") #"size_class_varying_non_cc") #n.ensembles = 100000
```

```{r Chunk 2.3.0, eval = TRUE}
# This sources "R/4.2GLUErun_part2_func_BCI.R"
source("R/4.3.GLUErun_part2_BCI.R")
GLUE_run(splevel = "off", goodness.fit = 0.3)
GLUE_run(splevel = "on", goodness.fit = 0.3)
```

```{r Chunk 2.4.0, eval = TRUE}
source("R/4.4.Best-fit_param_BCI.R")
bestfit.param(splevel = "on")
bestfit.param(splevel = "off")
```

@@

```{r Chunk 2.4.2, eval = TRUE}
source("R/4.6.udi.calculator.R")
udi.calculator(splevel = "on", dryseason = "on", rsq.thresh = 0.5) ## udi is not calculated below this rsq.thresh
udi.calculator(splevel = "off", dryseason = "on", rsq.thresh = 0.5)
```

```{r Chunk 2.4.4, eval = TRUE}
source("R/4.7.summarising_udi_by_sp_size.R")
summarise.udi(splevel = "on", dryseason = "on", rsq.thresh = 0.7)
summarise.udi(splevel = "off", dryseason = "on", rsq.thresh = 0.7)
```

>>>>

```{r Chunk 2.2.0, eval = FALSE}
source("R/4.1.GLUEsetup_part2_BCI.R")
GLUEsetup_part2(growth.type = "med", dbh.residuals = "off", solar.residuals = "off", 
                growth.selection = "size_class_predefined_cc_scaled") #"size_class_varying_non_cc") #n.ensembles = 100000
# growth.type = "med"; dbh.residuals = "off"; solar.residuals = "off"; growth.selection = "size_class_predefined_cc_scaled"
```

```{r Chunk 2.3.0, eval = TRUE}
# This sources "R/4.2GLUErun_part2_func_BCI.R"
source("R/4.3.GLUErun_part2_BCI.R")
GLUE_run(splevel = "off", goodness.fit = 0.3)
# GLUE_run(splevel = "on", goodness.fit = 0.3)
```

<!-- ```{r Chunk 2.4.0, eval = TRUE} -->
<!-- source("R/4.4.Best-fit_param_BCI.R") -->
<!-- # bestfit.param(splevel = "on") -->
<!-- bestfit.param(splevel = "off") -->
<!-- ``` -->

@@

```{r Chunk 2.4.2, eval = TRUE}
source("R/4.6.udi.calculator.R")
##---needs to be run manually on macbook for splevel = "off" and iso.subset = "off"---
# udi.calculator(splevel = "on", dryseason = "on", rsq.thresh = 0.5, iso.subset = "on") ## udi is not calculated below this rsq.thresh
# # splevel = "on"; dryseason = "off"; rsq.thresh = 0.5; iso.subset = "on"
# udi.calculator(splevel = "on", dryseason = "off", rsq.thresh = 0.5, iso.subset = "on") 
# udi.calculator(splevel = "off", dryseason = "on", rsq.thresh = 0.5, iso.subset = "on")
udi.calculator(splevel = "off", dryseason = "jan", rsq.thresh = 0.5, iso.subset = "on")
udi.calculator(splevel = "on", dryseason = "jan", rsq.thresh = 0.5, iso.subset = "on")
# udi.calculator(splevel = "off", dryseason = "1992", rsq.thresh = 0.5, iso.subset = "off") 
# udi.calculator(splevel = "on", dryseason = "1992", rsq.thresh = 0.5, iso.subset = "off")
```

```{r Chunk 2.4.4, eval = TRUE}
source("R/4.7.summarising_udi_by_sp_size.R")
# summarise.udi(splevel = "on", dryseason = "on", rsq.thresh = 0.5, root.selection = "on", iso.subset = "on")
# # splevel = "on"; dryseason = "off"; rsq.thresh = 0.5; root.selection = "on"; iso.subset = "off"
# summarise.udi(splevel = "on", dryseason = "off", rsq.thresh = 0.5, root.selection = "on", iso.subset = "on")
# summarise.udi(splevel = "off", dryseason = "on", rsq.thresh = 0.5, root.selection = "on", iso.subset = "on")
# summarise.udi(splevel = "off", dryseason = "off", rsq.thresh = 0.5, root.selection = "on", iso.subset = "on")
summarise.udi(splevel = "on", dryseason = "jan", rsq.thresh = 0.5, root.selection = "on", iso.subset = "on")
summarise.udi(splevel = "off", dryseason = "jan", rsq.thresh = 0.5, root.selection = "on", iso.subset = "on")
```
